---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(speedrunr)
```
# speedrunr

The goal of speedrunr is to easily access data from [speedrun.com](https://speedrun.com).

## Installation

You can install the released version of speedrunr from GitHub with:

``` r
remotes::install_github("jemus42/speedrunr")
```

## Example

Let's say you want to plot the times of all *Ocarina of TIme 100%* runs.  
Let's get started:

```{r, message=FALSE, error=FALSE}
library(dplyr)
library(knitr)
```


### Identifiyng the game you're looking for

You can either search for "Ocarina of Time", or supply `'oot'`, the game's abbreviation on speedrun.com.

```{r}
games <- get_games(name = "Ocarina of Time")

kable(games)
```

Turns out `j1l9qz1g` is the id we're looking for.

### Get the game's categories

```{r}
categories <- get_categories(id = "j1l9qz1g")

categories %>%
  select(-rules) %>%
  kable()
```

So apparently we're looking for `q255jw2o`, the full-game 100% category.

### Get the runs in that category

Now we can fetch the runs. By default, 100 runs are returned, ordered by submit date in descending order, so newest runs first.

```{r}
runs <- get_runs(game = "j1l9qz1g", category = "q255jw2o")
```

And now we can basically re-create the leaderboard, but including obsoleted runs:

```{r}
library(hms)

runs %>%
  arrange(time_primary) %>%
  head(20) %>%
  select(submitted, time_primary, player_url) %>%
  mutate(time_primary = hms(seconds = time_primary)) %>%
  kable()
```

Resolving user id's to usernames and e.g. platform id to platform name is to be implented.


## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.